---
title: "main"
output: pdf_document
---
Initialize

Import all modules & packages
```{r}

```

Aquire and clean data
```{r}
ghg_time <- read.csv(file.path(".","data","ghg_country_timeseries_df.csv"))
ghg_country <- read.csv(file.path(".","data","ghg_country_2018_df.csv"))
```

#####Part 1: Characterizing GHG trends from 1990 - 2018 (Will be done in Python)######
####Plot series #1 (a): Are there observable patterns (linear, exponential) of GHG emissions from 1990 - 2018? What do those patterns look like when countries are grouped by region or income?####

Plot series #1: Totals (i)
Plot #1 a i 1: Plot pattern of Total GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a i 2: Plot pattern of Total GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a i 3: Plot pattern of Total GHG emissions grouped by region. Find pattern
```{r}

```

Plot series #1: % of total (ii)
Plot #1 a ii 1: Plot pattern of % of total GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a ii 2: Plot pattern of % of total GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a ii 3: Plot pattern of % of total GHG emissions grouped by region. Find pattern
```{r}

```

Plot series #1: per capita (iii)
Plot #1 a ii 1: Plot pattern of per capita GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a ii 2: Plot pattern of per capita GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a ii 3: Plot pattern of per capita GHG emissions grouped by region. Find pattern
```{r}

```

####Part 2: Analyzing a snapshot (2018) of GHG emissions by country####
####Analysis #1: Are there observable differences in GHG emissions for 2018 amongst different country groupings (region and income groups)?####
####Analysis #1 a: Checking ANOVA test assumptions for region and income groupings, where the null hypothesis is that the per capita emissions are equal for the different groupings.####
Assumptions check for ANOVA test for region
```{r}

```
Assumptions check for ANOVA test for income
```{r}

```
####Analysis #1 b: ANOVA test for region and income groupings, where the null hypothesis is that the per capita emissions are equal for the different groupings.####

ANOVA test for region
```{r}

```
ANOVA test for income
```{r}

```

####Analysis #1 c: Box plots to understand which groupings are the most different####
```{r}

```
####Analysis #1 d: Perform t-tests for the most interesting differences. Arrive to conclusions####
```{r}

```

####Analysis #2: Which variables are related to GHG emissions? ####
####Analysis #2 a: Linear Regression analysis to understand relationships####
####Analysis #2 a i: Electricity #####
####Analysis #2 a i 1: Log(GHG Emissions) ~ Electricity ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Electricity + region
```{r}

```


####Analysis #2 a i 2: GHG Emissions per capita ~ Electricity ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Electricity + region
```{r}

```

####Analysis #2 a i 3: GHG Emissions % of total ~ Electricity ####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Electricity + region
```{r}

```

####Analysis #2 b i: Further exploration ####
```{r}

```
####Analysis #2 a ii: Land use (Agricultural, Arable or Permanent crops) #####
####Analysis #2 a ii 1: Log(GHG Emissions) ~ Land use ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Land use + region
```{r}

```

####Analysis #2 a ii 2: GHG Emissions per capita ~ Land use ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Land use + region
```{r}

```

####Analysis #2 a ii 3: GHG Emissions % of total ~ Land use ####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Land use + region
```{r}

```
####Analysis #2 b ii: Further exploration ####
```{r}

```

####Analysis #2 a iii: GDP or GDP Growth#####
####Analysis #2 a iii 1: Log(GHG Emissions) ~ GDP ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ GDP + region
```{r}

```

####Analysis #2 a iii 2: GHG Emissions per capita ~ GDP ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ GDP + region
```{r}

```

####Analysis #2 a iii 3: GHG Emissions % of total ~ GDP####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ GDP + region
```{r}

```

####Analysis #2 b iii: Further exploration ####
```{r}

```

####Analysis #2 a iv: Urban-to-rural ratio or population density#####
####Analysis #2 a iv 1: Log(GHG Emissions) ~ Population ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Population + region
```{r}

```

####Analysis #2 a iv 2: GHG Emissions per capita ~ Population####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Population + region
```{r}

```

####Analysis #2 a iv 3: GHG Emissions % of total ~ Population####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Population + region
```{r}

```

####Analysis #2 b iv: Further exploration ####
```{r}

```












