---
title: "main"
output: pdf_document
---
Initialize

Import all modules & packages
```{r}

```

Aquire and clean data
```{r}
ghg_time <- read.csv(file.path(".","data","ghg_country_timeseries_df.csv"))
ghg_country <- read.csv(file.path(".","data","ghg_country_2018_df.csv"))
# install.packages('sandwich')
library("regclass")
library(lmtest)
library(sandwich)
library("plyr")
```

#####Part 1: Characterizing GHG trends from 1990 - 2018 (Will be done in Python)######
####Plot series #1 (a): Are there observable patterns (linear, exponential) of GHG emissions from 1990 - 2018? What do those patterns look like when countries are grouped by region or income?####

Plot series #1: Totals (i)
Plot #1 a i 1: Plot pattern of Total GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a i 2: Plot pattern of Total GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a i 3: Plot pattern of Total GHG emissions grouped by region. Find pattern
```{r}

```

Plot series #1: % of total (ii)
Plot #1 a ii 1: Plot pattern of % of total GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a ii 2: Plot pattern of % of total GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a ii 3: Plot pattern of % of total GHG emissions grouped by region. Find pattern
```{r}

```

Plot series #1: per capita (iii)
Plot #1 a ii 1: Plot pattern of per capita GHG emissions for the world. Find pattern
```{r}

```
Plot #1 a ii 2: Plot pattern of per capita GHG emissions grouped by income. Find pattern
```{r}

```
Plot #1 a ii 3: Plot pattern of per capita GHG emissions grouped by region. Find pattern
```{r}

```

####Part 2: Analyzing a snapshot (2018) of GHG emissions by country####
####Analysis #1: Are there observable differences in GHG emissions for 2018 amongst different country groupings (region and income groups)?####
####Analysis #1 a: Checking ANOVA test assumptions for region and income groupings, where the null hypothesis is that the per capita emissions are equal for the different groupings.####
Assumptions check for ANOVA test for region
```{r}

```
Assumptions check for ANOVA test for income
```{r}

```
####Analysis #1 b: ANOVA test for region and income groupings, where the null hypothesis is that the per capita emissions are equal for the different groupings.####

ANOVA test for region
```{r}

```
ANOVA test for income
```{r}

```

####Analysis #1 c: Box plots to understand which groupings are the most different####
```{r}

```
####Analysis #1 d: Perform t-tests for the most interesting differences. Arrive to conclusions####
```{r}

```

####Analysis #2: Which variables are related to GHG emissions? ####
```{r}
# setup
#log_ghg_capita = log10(ghg_country$`Total greenhouse gas emissions per capita (kt of CO2 equivalent per person)`)
#log_ghg_tot = log10(ghg_country$`Total greenhouse gas emissions (kt of CO2 equivalent)`)
#log_ghg_pct = log10(ghg_country$`Total greenhouse gas emissions as % of Total (kt of CO2 equivalent)`)

log_ghg_pc = log(ghg_country$Total.greenhouse.gas.emissions.per.capita..kt.of.CO2.equivalent.per.person.)
log_ghg_tot = log(ghg_country$Total.greenhouse.gas.emissions..kt.of.CO2.equivalent.)
log_ghg_per = log(ghg_country$Total.greenhouse.gas.emissions.as...of.Total..kt.of.CO2.equivalent.)

analyze_model = function(data,model) {
  v <- vcovHC(model)
  robust.se <- sqrt(diag(v))
  result = cbind(summary(model)$coef,robust.se)
  result = transform(result, robust_t_value = Estimate / robust.se)
  rdf = nrow(data) - nrow(result)
  result = transform(result, robust_p_value = 2 * pt(abs(robust_t_value), rdf, lower.tail = FALSE))
  return (result)
}
```

####Analysis #2 a: Linear Regression analysis to understand relationships####
####Analysis #2 a i: Electricity #####
####Analysis #2 a i 1: Log(GHG Emissions) ~ Electricity ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Electricity + region
```{r}

```


####Analysis #2 a i 2: GHG Emissions per capita ~ Electricity ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Electricity + region
```{r}

```

####Analysis #2 a i 3: GHG Emissions % of total ~ Electricity ####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Electricity + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Electricity + region
```{r}

```

####Analysis #2 b i: Further exploration ####
```{r}

```
####Analysis #2 a ii: Land use (Agricultural, Arable or Permanent crops) #####
####Analysis #2 a ii 1: Log(GHG Emissions) ~ Land use ####
Clean data (remove rows with nulls)
```{r}
land_use_data = subset(ghg_country_2018_df, !is.na(`Forest area (% of land area)`))
land_use_data = subset(land_use_data, !is.na(`Agricultural land (% of land area)`))
land_use_data = subset(land_use_data, !is.na(`Arable land (% of land area)`))
land_use_data = subset(land_use_data, !is.na(Region))
land_use_data = subset(land_use_data, !is.na(`Income Level`))
land_use_data = subset(land_use_data, !is.na(`Land area (sq. km)`))
log_ghg_capita_land_use = log10(land_use_data$`Total greenhouse gas emissions per capita (kt of CO2 equivalent per person)`)

```

Start by plotting log GHG to different factors
```{r}
# Forest - no clear trend
plot(land_use_data$`Forest area (% of land area)`, log_ghg_capita_land_use)
# Arable - slight negative (strongest)
plot(land_use_data$`Arable land (% of land area)`, log_ghg_capita_land_use)
# Agricultural - slight negative
plot(land_use_data$`Agricultural land (% of land area)`, log_ghg_capita_land_use)
# Land area - maybe slight positive, harder to tell at smaller values
plot(land_use_data$`Land area (sq. km)`, log_ghg_capita_land_use)
plot(log10(land_use_data$`Land area (sq. km)`), log_ghg_capita_land_use)
```
Simple model with just land area (normal and log):
- Log(land area) shows not great linearity and just ok constant variance
  - Not statistically significant!
- Land area shows really bad constant variance. 
  - Statistically significant! Coefficient estimate of 4.537990e-08 at p-value 5.704285e-05 (using robust SE).
```{r}
land_model1a = lm(log_ghg_capita_land_use ~ I(log10(`Land area (sq. km)`)), data=land_use_data)
analyze_model(land_model1a)
plot(land_model1a)

land_model1b = lm(log_ghg_capita_land_use ~ `Land area (sq. km)`, data=land_use_data)
analyze_model(land_model1b)
plot(land_model1b)
```
Model with % arable land:
- Not great constant variance, ok normal errors, ok linearity
- Statistically significant! Slight negative coefficient (-0.006583616), robust p-value .006068752
```{r}
land_model2 = lm(log_ghg_capita_land_use ~ `Arable land (% of land area)`, data=land_use_data)
analyze_model(land_model2)
plot(land_model2)
```
Model with % agricultural land:
- Pretty good on assumptions, including constant variance
- Statistically significant! Slight negative coefficient (-0.00529277), robust p-value .0006613491
```{r}
land_model3 = lm(log_ghg_capita_land_use ~ `Agricultural land (% of land area)`, data=land_use_data)
analyze_model(land_model3)
plot(land_model3)
```
Model with % forest area:
- Pretty good on assumptions, ok constant variance
- NOT statistically significant.
```{r}
land_model4 = lm(log_ghg_capita_land_use ~ `Forest area (% of land area)`, data=land_use_data)
analyze_model(land_model4)
plot(land_model4)
```
Model with % arable land + agriculture:
- Pretty good on assumptions, ok constant variance
- NOT statistically significant.
```{r}
land_model5= lm(log_ghg_capita_land_use ~ `Arable land (% of land area)` + `Agricultural land (% of land area)`, data=land_use_data)
analyze_model(land_model5)
plot(land_model5)
```

```{r}
# high income and East Asian and Pacific as control
# sub-saharan africa has less effect on emissions than east asian and pacific having all the rest equal
null_model = lm(log_ghg_capita_land_use ~ factor(`Income Level`), data=land_use_data)

land_model = lm(log_ghg_capita_land_use ~ `Land area (sq. km)` + `Forest area (% of land area)` + `Agricultural land (% of land area)` + `Arable land (% of land area)` + factor(`Income Level`), data=land_use_data)

analyze_model(land_model)
plot(land_model)

# F-test with region/income as null model!
# waldtest(null_model, land_model, test="Chisq", vcov=vcovHC)
waldtest(null_model, land_model, test="F")
```
Are robust methods or transformations necessary?
```{r}
VIF(land_model)

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Land use + region
```{r}

```

####Analysis #2 a ii 2: GHG Emissions per capita ~ Land use ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Land use + region
```{r}

```

####Analysis #2 a ii 3: GHG Emissions % of total ~ Land use ####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Land use + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Land use + region
```{r}

```
####Analysis #2 b ii: Further exploration ####
```{r}

```

####Analysis #2 a iii: GDP or GDP Growth#####
####Analysis #2 a iii 1: Log(GHG Emissions) ~ GDP ####
Check if assumptions are being met for Log(Emissions)
```{r}
log_ghg_pc = log(ghg_country$Total.greenhouse.gas.emissions.per.capita..kt.of.CO2.equivalent.per.person.)
log_ghg_tot = log(ghg_country$Total.greenhouse.gas.emissions..kt.of.CO2.equivalent.)
log_ghg_per = log(ghg_country$Total.greenhouse.gas.emissions.as...of.Total..kt.of.CO2.equivalent.)


## Assumption check for per capita emissions
economy_model_pc <- lm(log_ghg_pc ~ GDP.growth..annual... + GDP..current.US.. + GDP.per.capita..constant.2015.US.. + factor(Region) + factor(Income.Level), data = ghg_country)
analyze_model(ghg_country,economy_model_pc)
## ASSUMPTIONS ARE  MET
count(ghg_country,vars="Region")
count(ghg_country,vars="Income.Level")
VIF(economy_model_pc)
```

```{r}
## Assumption check for total emissions
economy_model_tot <- lm(log_ghg_tot ~ GDP.growth..annual... + GDP..current.US.. + GDP.per.capita..constant.2015.US.. + factor(Region) + factor(Income.Level), data = ghg_country)
plot(economy_model_tot)
summary(economy_model_tot)
```
ASSUMPTIONS ARE NOT MET

```{r}
## Assumption check for percentage emissions
economy_model_percentage <- lm(log_ghg_per ~ GDP.growth..annual... + GDP..current.US.. + GDP.per.capita..constant.2015.US.. + factor(Region) + factor(Income.Level), data = ghg_country)
plot(economy_model_percentage)
summary(economy_model_percentage)
```
ASSUMPTIONS ARE NOT MET

Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ GDP + region
```{r}

```

####Analysis #2 a iii 2: GHG Emissions per capita ~ GDP ####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ GDP + region
```{r}

```

####Analysis #2 a iii 3: GHG Emissions % of total ~ GDP####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ GDP + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ GDP + region
```{r}

```

####Analysis #2 b iii: Further exploration ####
```{r}

```

####Analysis #2 a iv: Urban-to-rural ratio or population density#####
####Analysis #2 a iv 1: Log(GHG Emissions) ~ Population ####
Check if assumptions are being met for Log(Emissions)
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
Log(GHG Emissions) ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
Log(GHG Emissions) ~ Population + region
```{r}

```

####Analysis #2 a iv 2: GHG Emissions per capita ~ Population####
Check if assumptions are being met for GHG Emissions per capita
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions per capita ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions per capita ~ Population + region
```{r}

```

####Analysis #2 a iv 3: GHG Emissions % of total ~ Population####
Check if assumptions are being met for GHG Emissions % of total
```{r}

```
Are robust methods or transformations necessary?
```{r}

```
Create the linear regression model
```{r}

```
Include stratification by income and perform F-tests.
GHG Emissions % of total ~ Population + Income
```{r}

```
Include stratification by region and perform F-tests.
GHG Emissions % of total ~ Population + region
```{r}

```

####Analysis #2 b iv: Further exploration ####
```{r}

```












